---
title: 'Tutorial_4: Figure 3'
author: "Wei-Chun Chou"
advisor: "Zhoumeng Lin"
date: "June, 2020"
fontsize: 12pt
output:
  html_document:
    theme: cerulean 
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## knitr::opts_knit$set(root.dir = "C:/Users/weichunc/Dropbox/PostDoc_KSU/Project/Project 1- PFOX PBPK/PART IV-Pregnacy PBPK mdoel/Manuscript/V2/Additional files/Results/PlotCode")
knitr::opts_knit$set(root.dir = "C:/Users/zhoumeng/Dropbox/Transfer/Wei-Chun/Project 2 Gestational/V3/Additional files/Results/PlotCode")
```

# Introduction
The tutorial aims to guide you to step-by-step reproduce Figure 3 in the manuscript. We conducted a loacal sensivity analysis to find the most influence parameters to model output. 

# Prerequisites
Before running your model, you should set up your working directory, compile the PBPK model, install all required packages and input needed datasets. The model file and datasets can be found in the additional files. 

## Setting up your working directory
Before running, you should change your working directory to the **PlotCode** folder. You can use two ways to change your working directory as follow:

1. Use RStudio: use the menu to change your working directory under **Session > Set Working Directory > Choose Directory**. <br>
2. Use R function: use the R function `setwd()` to change the path to your working directory.  

## Loading required R packages  
The list of R packages should be installed first prior to the simulation. If you have not installed these packages (listed below), please install these packages to your Rstudio using the R function `require (" ")` and then use `library` open it.

```{r echo=TRUE, message=FALSE}
##  Loading requried R packages
library(mrgsolve)    ## R-package for Loading mrgsolve code into R via mcode from the 'mrgsolve' pckage
library(magrittr)    ## R-package for the pipe, %>% , comes from the magrittr package by Stefan Milton Bache
library(dplyr)       ## R-package for transform and summarize tabular data with rows and columns; %>%
library(tidyverse)   ## R-package for transform and summarize tabular data with rows and columns; %>%
library(ggplot2)     ## R-package for GGplot
library(FME)         ## R-package for model fitting
library(minpack.lm)  ## R-package for model fitting
library(gridExtra)   ## R-package for function "grid.arrange"
```

## Read mrgsolve-based PBPK Model R file
The rat pre-pregnant, gestational and lactational PBPK model were written in `RMod.R` file. Before compiling the model, please conduct/call this file using R function `source`. 

```{r}
## Input mrgsolve-based PBPK Model
source (file = "RMod.R")  ## input the rat model for nonpregnnat, geatation and lactation
source (file = "HMod.R")  ## input the human model for nonpregnnat, geatation and lactation

```

## Complie mrgsolve-based PBPK Model
Read the code and build these mrgsolve-based PBPK models. You should make sure all models are built correctly. 

```{r}
## Build mrgsolve-based PBPK Model
PreGmod_R <- mcode ("PreG_RatPBPK.code", PreG_RatPBPK.code)
Gmod_R    <- mcode ("GRatPBPK.code", GRatPBPK.code)
Lmod_R    <- mcode ("LRatPBPK.code", LRatPBPK.code)
PreGmod_H <- mcode ("PreGHumanPBPK.code", PreGHumanPBPK.code) 
Gmod_H    <- mcode ("GHumanPBPK.code", GHumanPBPK.code)
Lmod_H    <- mcode ("LHumanPBPK.code", LHumanPBPK.code)
```

## Loading datasets
In this step, you need to input the .csv file to the Rstudio. The function `read.csv` can be used to read the csv files into R
```{r}
RDat <- read.csv(file = "Data_R.csv")
HDat <- read.csv(file = "Data_H.csv")

```

## Loading Fit results from rds files to obtain parameter values
```{r}
GFit_R <- readRDS(file = "GFit_R.rds")
LFit_R <- readRDS(file = "LFit_R.rds")
GFit_H <- readRDS(file = "GFit_H.rds")
LFit_H <- readRDS(file = "LFit_H.rds")
```
## Input mrgsolve-based PBPK Model as a prediction function
```{r}
source (file = "Pred_Rat.R")
source (file = "Pred_H.R")
```

# List all parameters and later used in sensitivity analysis
We list all parameters used in gestational and lactational model and then conduct the sensitivity analysis to find sensitive parameters.

- Rat.theta.G: Parameters used in the rat gestational model
- Rat.theta.L: Parameters used in the rat lactational model
- Human.theta.G: Parameters used in the human gestational model
- Human.theta.L: Parameters used in the human lactational model

```{r}
Rat.theta.G <- log(c(
# Physiological parameters
    BW                             = 0.185,
    QLC                            = 0.183,
    QKC                            = 0.141,
    QMC                            = 0.002,
    QFC                            = 0.07,
    VLC                            = 0.035,
    VKC                            = 0.0084,
    VMC                            = 0.01,
    VFC                            = 0.07,
    VPlasC                         = 0.0466,
    VFilC                          = 8.4E-4,
    VPTCC                          = 1.35E-4,
    GFRC                           = 41.04,
    QLC_Fet                        = 0.061,
    VPlasC_Fet                     = 0.047,
# Chemical-specific parameters (final mean values)
    Vmax_baso_invitro              = 221, # fitting parameters
    Km_baso                        = 19.9, # fitting parameters
    Vmax_apical_invitro            = 1808,
    Km_apical                      = 278,                        
    RAFbaso                        = 4.15,                       
    RAFapi                         = 1.90,
    KeffluxC                       = 2.09,
    KbileC                         = 0.007, # fitting parameters
    KurineC                        = 1.6,                        
    Free                           = 0.019, #fitting parameters
    PL                             = 3.17,  #fitting parameters
    PK                             = 0.80,
    PM                             = 0.16,
    PF                             = 0.13,
    PRest                          = 0.22,
    PPla                           = 0.41,
    K0C                            = 1,
    Kabsc                          = 2.12,
    Kdif                           = 1e-3,                       
    KunabsC                        = 7.05e-5,
    Ktrans1C                       = 1.27, # fitting parameters
    Ktrans2C                       = 1,
    Ktrans3C                       = 0.23, # fitting parameters
    Ktrans4C                       = 0.001,
    Free_Fet                       = 0.022, 
    PL_Fet                         = 1.30, # fitting parmaeters
    PRest_Fet                      = 0.11  # fitting parameters
))

Rat.theta.L <- log(c(
# Physiological parameters
    BW0                            = 0.247,
    QLC0                           = 0.196,
    QKC0                           = 0.1161,
    QMC0                           = 0.0887,
    QFC                            = 0.07,
    VLC0                           = 0.046,
    VKC0                           = 0.011,
    VMC0                           = 0.049,
    VFC0                           = 0.1245,
    VPlasC                         = 0.0466,
    VFilC                          = 8.4E-4,
    VPTCC                          = 1.35E-4,
    GFRC                           = 41.04,
# Chemical-specific parameters (final mean values)
    Vmax_baso_invitro              = 393.45,
    Km_baso                        = 27.2,  
    Vmax_apical_invitro            = 4141,# fitting parameter
    Km_apical                      = 278,
    RAFbaso                        = 1.90,
    RAFapi                         = 4.15,
    KeffluxC                       = 2.09,
    KbileC                         = 0.0026,
    KurineC                        = 1.60,
    Free                           = 0.0037, # fitting parameter
    PL                             = 2.72,   # fitting parameter
    PK                             = 0.8,
    PM                             = 0.16,
    PF                             = 0.13,
    PRest                          = 0.033,# fitting parameter
    PMilkM                         = 1.9,  
    PMilkP                         = 0.11,
    PAMilkC                        = 0.5,
    KMilk0                         = 0.28, # fitting parameter 
    K0C                            = 1,
    KabsC                          = 2.12,
    KunabsC                        = 7.05e-5,
    Kdif                           = 1e-3,
    Free_pup                       = 0.022,
    PL_pup                         = 2.55,  # fitting parameter
    PK_pup                         = 0.80,
    PRest_pup                      = 0.16,
    KabsC_pup                      = 2.12,
    KbileC_pup                     = 0.0026,
    KurineC_pup                    = 1.6,
    KeffluxC_p                     = 2.09,
    Kdif_pup_0                     = 0.001,
    Vmax_baso_invitro_p            = 393.45,
    Km_baso_p                      = 27.2,
    Vmax_apical_invitro_p          = 1808,
    Km_apical_p                    = 278
))

Human.theta.G <- log(c(
# Physiological parameters
    BW                             = 67.7,
    QCC                            = 16.4,
    QLC                            = 0.25, 
    QKC                            = 0.141,
    QMC                            = 0.027,
    QFC                            = 0.052,
    VLC                            = 0.026,
    VKC                            = 0.004,
    VFC                            = 0.214,
    VMC                            = 0.0062,
    VFileC                         = 8.4E-4,  
    VPTCC                          = 1.35E-4, 
    GFRC                           = 24.19,
# Chemical-specific parameters (final mean values)
    Vmax_baso_invitro              = 479,                      
    Km_baso                        = 20.1,
    Vmax_apical_invitro            = 51803,
    Km_apical                      = 248,   # fitting parameter
    RAFapi                         = 0.001,
    RAFbaso                        = 1,                        
    KeffluxC                       = 0.15,
    KbileC                         = 1.3e-4,
    KurineC                        = 0.17,
    Free                           = 0.0027, # fitting parameter
    PL                             = 2.03,
    PK                             = 1.26,
    PM                             = 0.13,
    PF                             = 0.16,
    PRest                          = 0.20,
    PPla                           = 0.13, # fitting parameter
    K0C                            = 1,
    Kabsc                          = 2.12,
    Kdif                           = 0.001,
    KunabsC                        = 7.05e-5,
    Ktrans1C                       = 0.79, # fitting parameter
    Ktrans2C                       = 1.12, # fitting parameter
    Ktrans3C                       = 0.006,
    Ktrans4C                       = 0.001,
    Free_Fet                       = 0.0038, # fitting parameter
    PL_Fet                         = 0.58,  # fitting parameter
    PRest_Fet                      = 2.3   # fitting parameter
))


Human.theta.L <- log(c(
# Physiological parameters
    BW0                            = 68.05,
    QCC                            = 16.4,
    QLC                            = 0.25,
    QKC                            = 0.141,
    QMC                            = 0.027,
    QFC                            = 0.052,
    VLC                            = 0.026,
    VKC                            = 0.004,
    VMC                            = 0.0062,
    VMilk                          = 0.008,
    VFilC                          = 8.4E-4,
    VPTCC                          = 1.35E-4,
    GFRC                           = 24.19,
# Chemical-specific parameters (final mean values)
    Vmax_baso_invitro              = 479,
    Km_baso                        = 20.1,
    Vmax_apical_invitro            = 51803,
    Km_apical                      = 64.4,
    RAFbaso                        = 1,
    RAFapi                         = 0.525, # fitting parameter
    KeffluxC                       = 0.15, 
    KbileC                         = 1.3e-4,
    KurineC                        = 0.096,
    Free                           = 0.037, # fitting parameter
    PL                             = 2.03,
    PK                             = 1.26,
    PM                             = 0.13,
    PF                             = 0.16,
    PRest                          = 0.20, 
    PMilkM                         = 1.9,
    PMilkP                         = 0.11,
    PAMilkC                        = 0.0028, # fitting parameter
    K0C                            = 1,
    KabsC                          = 2.12,
    KunabsC                        = 7.05e-5,
    Kdif                           = 0.001,
    Free_neo                       = 0.014,
    PL_neo                         = 2.03,
    PK_neo                         = 1.26,
    PRest_neo                      = 0.20,
    Vmax_baso_invitro_neo          = 479,
    Km_baso_neo                    = 20.1,
    Vmax_apical_invitro_neo        = 51803,
    Km_apical_neo                  = 64.4,
    KeffluxC_neo                   = 0.150,
    Kdif_neo                       = 0.001,
    KbileC_neo                     = 1.3e-4,
    KurineC_neo                    = 0.001
))

```

# Define the prediction function (i.e., the PBPK model)
The prediction function is defined here and then used in the sensitivity analysis later.

```{r}
pred.Rat <- function(Gpars, Lpars, DOSE) {
    
## Get out of log domain
Gpars <- lapply(Gpars, exp)           ## Return a list of exp (parametrs for gestational model) from log scale
Lpars <- lapply(Lpars, exp)           ## Return a list of exp (parametrs for lactational model) from log scale
    
## Exposure scenario for gestational exposure
GBW          = 0.267                  ## Body weight before gestation
tinterval    = 24                     ## Time interval; 
GTDOSE       = 22                     ## Total dosing/Dose times; Repeat oral dose 
GDOSE        = DOSE                   ## Repeat oral dose 
GDOSEoral    = GDOSE*GBW              ## Amount of oral dose
    
# To create an exposure scenario
Gex.oral <- ev (ID   = 1,             ## One individual
                amt  = GDOSEoral,     ## Amount of dose 
                ii   = tinterval,     ## Time interval
                addl = GTDOSE - 1,    ## Additional dosing 
                cmt  = "AST",         ## The dosing compartment: AST Stomach  
                replicate = FALSE)    ## No replicate
    
Gtsamp  = tgrid(0, tinterval*(GTDOSE - 1) + 24*1, 1) ## Simulation time 
    
## Simulation of exposure scenario
Gout <- 
    Gmod_R %>%
    param (Gpars) %>%
    update(atol = 1E-6, maxsteps = 500000) %>%          
    mrgsim_d (data = Gex.oral, tgrid = Gtsamp)
    
Goutdf = cbind.data.frame(Time   = Gout$time, 
                          CPlas  = Gout$AUC_CPlas, 
                          CPlas_pup = Gout$Plasma_Fet,
                          AUC_CPlas = Gout$AUC_CPlas,
                          AUC_CPlas_pup = Gout$AUC_CPlas_Fet)
    
## Exposure scenario for lactational exposure; through PND0 - PND21 (end of lactation)
LBW          = 0.267                  ## Rat body weight on PND0 (GD21); from Thibodeaux et al., 2003
tinterval    = 24                     ## Time interval; 
LTDOSE       = 22                     ## Total dosing/Dose times; Repeat oral dose from PND0 - PND21
LDOSE        = DOSE                   ## Repeat oral dose of GDOSE mg/kg/day;  
LDOSEoral    = LDOSE*LBW              ## Amount of oral dose
    
    
# To create a data set of 1 subject receiving DOSEoral every 24 hours
Lex.oral <- ev (ID   = 1,       ## One individual
            amt  = LDOSEoral,    ## Amount of dose 
            ii   = tinterval,    ## Time interval
            addl = LTDOSE - 1,   ## Additional doseing 
            cmt  = "AST",        ## The dosing compartment: AST Stomach  
            replicate = FALSE)   ## No replicate
    
Ltsamp       = tgrid(0, tinterval*(LTDOSE - 1) + 24*2, 1) ## Simulation time from PND0 to PND21 with dosing of 1 + (LTDOSE - 1) + 2 days (No dosing)
    
    
Lout <- Lmod_R %>% 
        param (Lpars) %>%
        update(atol = 1E-6, maxsteps = 500000) %>%          
        mrgsim_d (data = Lex.oral, tgrid = Ltsamp) 
    
Loutdf = cbind.data.frame(Time      = Lout$time, 
         CPlas     = Lout$Plasma,CPlas_pup = Lout$Plasma_pup,
         AUC_CPlas = Lout$AUC_CPlas,AUC_CPlas_pup = Lout$AUC_CPlas_pup)
    
Goutdf <- Goutdf %>% filter (Time == 21*24) ## The model output on GD21
Loutdf <- Loutdf %>% filter (Time == 21*24) ## The model output on PND21
    
return (list("G" = Goutdf, "L" = Loutdf))
}



pred.Human <- function(Gpars, Lpars, DOSE) {
    
## Get out of log domain
Gpars <- lapply(Gpars, exp)## Return a list of exp (parametrs for gestational model) from log scale
Lpars <- lapply(Lpars, exp)## Return a list of exp (parametrs for lactational model) from log scale
    
## Exposure scenario for gestational exposure
GBW          = 67                 ## Body weight during gestation 
tinterval    = 24                 ## Time interval; 
GTDOSE       = 7*40               ## Total dosing/Dose times; 
GDOSE        = DOSE               ## Input oral dose  
GDOSEoral    = GDOSE*GBW          ## Amount of oral dose
    
# To create exposure scenario
Gex.oral <- ev (ID   = 1,         ## One individual
            time = 0,             ## Dosing start time (GD0)
            amt  = GDOSEoral,     ## Amount of dose 
            ii   = tinterval,     ## Time interval
            addl = GTDOSE - 1,    ## Additional doseing 
            cmt  = "AST",         ## dosing: AST Stomach  
            replicate = FALSE)    ## No replicate
    
Gtsamp  = tgrid(0, tinterval*(GTDOSE - 1) + 24*1, 1) ## Simulation time 
    
## Simulation of exposure scenario
Gout <- 
    Gmod_H %>%
    param (Gpars) %>%
    update(atol = 1E-3, maxsteps = 500000) %>%          
    mrgsim_d (data = Gex.oral, tgrid = Gtsamp)

    Goutdf = cbind.data.frame(Time   = Gout$time, 
                              CPlas  = Gout$AUC_CPlas, CPlas_pup = Gout$CordB,
                              AUC_CPlas = Gout$AUC_CPlas,AUC_CPlas_pup = Gout$AUC_CPlas_Fet)
    
    
## Exposure scenario for lactational exposure;  (to the end of lactation)
LBW          = 67                     ## Rat body weight on PND0 
tinterval    = 24                     ## Time interval
LTDOSE       = 41*7                   ## Total dosing/Dose times
LDOSE        = DOSE                   ## Repeat oral dose   
LDOSEoral    = LDOSE*LBW              ## Amount of oral dose (mg)
    
    
# To create a data set of 1 subject receiving DOSE every 24 hours
Lex.oral <- ev (ID   = 1,             ## One individual
                amt  = LDOSEoral,     ## Amount of dose 
                ii   = tinterval,     ## Time interval
                addl = LTDOSE - 1,    ## Addtional doseing 
                cmt  = "AST",         ## compartment: AST Stomach  
                replicate = FALSE)    ## No replicate
    
Ltsamp = tgrid(0, tinterval*(LTDOSE - 1) + 24*2, 1) ## Simulation time

Lout <- Lmod_H %>% # Lactational model
param (Lpars) %>% # Update the parameter list with pars
update(atol = 1E-3, maxsteps = 500000) %>% # Atol: absolute tolerance parameter; hmax: The maximum step size; maxstep: maximum number of steps the solver will take when advancing from one time to the next         
mrgsim_d (data = Lex.oral, tgrid = Ltsamp) 
    
## Extract the concentration 
Loutdf = cbind.data.frame(
         Time      = Lout$time, 
         CPlas     = Lout$Plasma, CPlas_neo = Lout$CPneo,
         AUC_CPlas = Lout$AUC_CPlas,AUC_CPlas_pup = Lout$AUC_CPlas_neo)
    
Goutdf <- Goutdf %>% filter (Time == 39*24*7) ## Gestational model output on GA39 (common sampling time in biomonitoring studies)
Loutdf <- Loutdf %>% filter (Time == 25*24*7) ## Lactational model output on 25 weeks after birth (typically depends on sampling time from the literature)
return (list("G" = Goutdf, "L" = Loutdf))
    
}
```

# Extract the optimized parameters and instaed of initial parameters
We adopt the optimized parameters from the object of `GFit_R`, `LFit_R` for rats and `GFit_H`, `LFit_H` for humans

```{r}
R.par.G <- GFit_R$par
R.par.L <- LFit_R$par
H.par.G <- GFit_H$par
H.par.L <- LFit_H$par

Rat.theta.G[names(R.par.G)]  <- as.numeric(R.par.G) 
Rat.theta.L[names(R.par.L)]  <- as.numeric(R.par.L) 
Human.theta.G[names(H.par.G)]<- as.numeric(H.par.G) 
Human.theta.L[names(H.par.L)]<- as.numeric(H.par.L) 
```

# Define the sensitivity function
The function (`NSC_GCA` and `NSC_LCA`) is used to analyze the normalized sensitivity coefficient

```{r}
NSC_func <- function (Gpars, Lpars, Pred, DOSE) {
nG <- length(Gpars)
nL <- length(Lpars)
NSC_GCA     = matrix(NA, nrow = length(Gpars) , ncol = 2)
NSC_LCA     = matrix(NA, nrow = length(Lpars) , ncol = 2)

for (i in 1:nG) {
Gpars.new      <- Gpars %>% replace(i, log(exp((Gpars[i]))*1.01))
Rnew.G         <- Pred(Gpars.new, Lpars, DOSE)
R.G            <- Pred(Gpars, Lpars, DOSE)
delta.Gpars    <- exp(Gpars[i])/(exp(Gpars[i])*0.01)
        
## Estimated the AUC
AUC.GCA.new       =  Rnew.G$G %>% select (AUC_CPlas)
AUC.GCA.ori       =  R.G$G    %>% select (AUC_CPlas)
AUC.GCA_pup.new   =  Rnew.G$G %>% select (AUC_CPlas_pup)
AUC.GCA_pup.ori   =  R.G$G    %>% select (AUC_CPlas_pup)
        
delta.AUC.GCA     =  AUC.GCA.new - AUC.GCA.ori
delta.AUC.GCA_pup =  AUC.GCA_pup.new - AUC.GCA_pup.ori
        
NSC_GCA [i, 1]   <- as.numeric((delta.AUC.GCA/AUC.GCA.ori) * delta.Gpars)
NSC_GCA [i, 2]   <- as.numeric((delta.AUC.GCA_pup /AUC.GCA_pup.ori) * delta.Gpars)
        
    }
for (j in 1:nL) {
Lpars.new      <- Lpars %>% replace(j, log(exp(as.numeric(Lpars[j]))*1.01))
Rnew.L         <- Pred(Gpars, Lpars.new, DOSE)
R.L            <- Pred(Gpars, Lpars, DOSE)
delta.Lpars    <- exp(Lpars[j])/(exp(Lpars[j])*0.01)
        
## Estimate the AUC
AUC.LCA.new       =  Rnew.L$L %>% select (AUC_CPlas)
AUC.LCA.ori       =  R.L$L    %>% select (AUC_CPlas)
AUC.LCA_pup.new   =  Rnew.L$L %>% select (AUC_CPlas_pup)
AUC.LCA_pup.ori   =  R.L$L    %>% select (AUC_CPlas_pup)
        
delta.AUC.LCA     =  AUC.LCA.new - AUC.LCA.ori
delta.AUC.LCA_pup =  AUC.LCA_pup.new - AUC.LCA_pup.ori
        
NSC_LCA [j, 1]<- as.numeric((delta.AUC.LCA/AUC.LCA.ori) *delta.Lpars)
NSC_LCA [j, 2]<- as.numeric((delta.AUC.LCA_pup /AUC.LCA_pup.ori) *delta.Lpars)
        
    }
    return (list(NSC_GCA = NSC_GCA, NSC_LCA = NSC_LCA))
}

```

# Manipulate the data for the use in plotting
We use the code (listed below) to analyize the normalized sensitivity coefficient for rat and human model during gestation and lactation and gather the information to plot the dataset.

- NSC_GCA_R: The normalized sensitivity coefficient for rat gestational model.
- NSC_LCA_R: The normalized sensitivity coefficient for rat lactational model.
- NSC_GCA_H: The normalized sensitivity coefficient for human gestational model.
- NSC_LCA_H: The normalized sensitivity coefficient for human lactational model.

```{r}
## Gather all the data for plotting
A <- NSC_func (Rat.theta.G, Rat.theta.L, pred.Rat, 0.1)
B <- NSC_func (Human.theta.G, Human.theta.L, pred.Human, 1.9E-7)

rownames (A$NSC_GCA)  = names(Rat.theta.G)
colnames (A$NSC_GCA)  = c("NSC_CPlas", "NSC_CPlas_pup")
rownames (A$NSC_LCA)  = names(Rat.theta.L)
colnames (A$NSC_LCA)  = c("NSC_CPlas", "NSC_CPlas_pup")

rownames (B$NSC_GCA)  = names(Human.theta.G)
colnames (B$NSC_GCA)  = c("NSC_CPlas", "NSC_CPlas_pup")
rownames (B$NSC_LCA)  = names(Human.theta.L)
colnames (B$NSC_LCA)  = c("NSC_CPlas", "NSC_CPlas_pup")

NSC_GCA_R <- data.frame(A$NSC_GCA)
NSC_LCA_R <- data.frame(A$NSC_LCA)
NSC_GCA_H <- data.frame(B$NSC_GCA)
NSC_LCA_H <- data.frame(B$NSC_LCA)


# Manipulate the data for the use in plotting
NSC_GCA_R<- NSC_GCA_R %>% gather(key = "matrix", value = "value")  %>% mutate (Pars = rep (names(Rat.theta.G),2)) %>% mutate (Pregnacy = "Gestation_R")
NSC_LCA_R<- NSC_LCA_R %>% gather(key = "matrix", value = "value")  %>% mutate (Pars = rep (names(Rat.theta.L),2)) %>% mutate (Pregnacy = "Lactation_R")
NSC_GCA_H<- NSC_GCA_H %>% gather(key = "matrix", value = "value")  %>% mutate (Pars = rep (names(Human.theta.G),2)) %>% mutate (Pregnacy = "Gestation_H")
NSC_LCA_H<- NSC_LCA_H %>% gather(key = "matrix", value = "value")  %>% mutate (Pars = rep (names(Human.theta.L),2)) %>% mutate (Pregnacy = "Lactation_H")

NSC_total <- rbind (NSC_GCA_H, NSC_LCA_H,NSC_GCA_R, NSC_LCA_R) 

label <- c("Human gestational model", "Human lactational model", "Rat gestational model", "Rat lactational model")
names(label) <- c("Gestation_H", "Lactation_H","Gestation_R", "Lactation_R")

```

# Find sensitivity parameters
You can use the code listed below to find the sensitive parameters (the absolute normalized sensitivity coefficient > 0.2) for plasma AUC of rats and humans during gestation and lactation.

- G_rat_senpars: The sensitive parameters for rat gestational model
- L_rat_senpars: The sensitive parameters for rat lactational model
- G_H_senpars: The sensitive parameters for human gestational model
- L_H_senpars: The sensitive parameters for human lactational model

```{r}
G_rat_senpars <- unique (NSC_GCA_R %>% filter (abs(value) > 0.2) %>% select(Pars))
L_rat_senpars <- unique (NSC_LCA_R %>% filter (abs(value) > 0.2) %>% select(Pars))
G_H_senpars   <- unique (NSC_GCA_H %>% filter (abs(value) > 0.2) %>% select(Pars))
L_H_senpars   <- unique (NSC_LCA_H %>% filter (abs(value) > 0.2) %>% select(Pars))
```

# Make a sensitivity plot 
```{r p1, warning=FALSE, fig.height=6, fig.width=6}
p1<- ggplot(data = NSC_total%>%filter (abs(value)>0.01), aes(x = Pars, y = value)) +
geom_bar (aes(fill = matrix), 
          position = "dodge", stat="identity", show.legend = TRUE) +  
facet_wrap(~ Pregnacy,  scales = "free_y", labeller = labeller(Pregnacy = label)) +
scale_y_continuous(expand=c(0,0),limits = c(-1, 1)) +
coord_flip()

## Add the font to font database
windowsFonts("Times" = windowsFont("Times New Roman"))
Plot_theme <-
theme_bw () +  
theme (
text = element_text (family = "Times"),   # text front (Time new roman)
axis.text.x  = element_text (size = 10, colour = "black", face = "bold"),    
axis.text.y  = element_text (size = 10, colour = "black", face = "bold"),    
axis.title   = element_blank(),   
strip.text.x = element_text(size = 12, face = "bold", colour = "black"),
legend.position ='none') 
   

p1 <- p1 + Plot_theme+ xlab("") + ylab("") 

p1
```


# Save the figure
Save your figures using `ggsave()`. In the `ggsave` function, you should set up the your path to save your figure in the local drive.  

```{r}
# ggsave("Fig.3.tiff",scale = 1,
#        plot = p1 ,
#        path = "C:/Users/weichunc/Desktop",
#        width = 20, height = 25, units = "cm", dpi = 320)

```






